### 2016-04-29 paper/paper.tex
new idea/rewrite of Pay-to-DDOS

If DDoSCoin accepted proofs against any TLS 1.2 server, miners would be
incentivized to solve local challenges rather than remote ones, leading to the
proof-of-work being a computational puzzle, rather than one based on
participation in a network denial of service. Thus, DDoSCoin must have a way to
agree on what victims are acceptable targets for the proofs-of-work to be considered
valid.

One simple way is to hardcode a set of victim certificates into the protocol.
For example, DDoSCoin's published code could contain the identities of
Facebook's servers, and only incentivize attacks against them. However, there
are many attackers that might feel uncomfortable attacking Facebook, but would
be willing to participate in attacks against other websites. In addition, having
only a single or small set of websites is a risk to DDoSCoin: if those websites
all go offline or successfully mitigate the attacks (such as by disabling TLS),
no future DDoSCoin blocks can be mined, and the currency will stall. At this
point, all DDoSCoins in circulation would become nearly worthless, as there
would be no way to safely transact them.

These issues lead to a few subtle requirements for choosing valid victims.
First, there must be \emph{limits} on who is allowed to be a victim, otherwise
miners can create local computational puzzles. At the same time, there must be
\emph{enough} targets in order to be robust. Similarly, the list of victims must
be \emph{flexible} in order to prevent a stalled blockchain through downed or
propery defended servers.

To address these issues, we propose two mechanisms the DDoSCoin protocol can
employ.

@@

In order to allow the set of victims to be updated, DDoSCoin could allow payment
for targetting specific servers. To accomplish this, DDoSCoin introduces a new
payment opcode, PAY\_TO\_DDOS, that can be used in transactions subject to
certain constraints. This opcode takes one argument: a string representing a
domain name that the payer wishes to add to the set of victim servers. The
transaction has no other parameters, but its value must be greater than the
coinbase reward a miner would normally receive, and it must carry a
non-negligble transaction fee. Once this transaction is stored in a valid block,
the specified domain name is temporarily added to the list of allowed victims.
The first miner to mine a block with that domain as the victim must specify the
PAY\_TO\_DDOS transaction as an input to its coinbase transaction (with any
arbitrary output address), and have no other coinbase transactions. In other
words, the miner collects the value in the PAY\_TO\_DDOS transaction in lieu of
the normal block reward.

The observant reader will notice that nothing stops the payer of the
PAY\_TO\_DDOS transaction and the miner that it goes to from being the same
entity. Indeed, a miner could create a PAY\_TO\_DDOS transaction with a victim
domain that only it has access to, ensuring that it will be able to mine the
block without competition, and collect its own payment. However, this will not
net the miner new coins (\TK beyond any transaction fees collected? But we could
make this block contain no transactions), as the coinbase transaction is
replaced with its own PAY\_TO\_DDOS input.

@@

>>>>

If DDoSCoin accepted proofs against any TLS 1.2 server, miners would be
incentivized to set up signed TLS servers locally, and focus exclusively on
solving those challenges instead of remote ones, leading to the
proof-of-work being a computational puzzle rather than one based on
participation in a network denial of service. Thus, DDoSCoin must have a way to
agree on what victims are acceptable targets for the proofs-of-work to be considered
valid. Similarly, it is important to focus the denial-of-service effort toward a
single or small number of victims in order to have the most impact.

One simple way to is to hardcode a set of victim certificates into the protocol.
For example, DDoSCoin's published code could contain the identities of
Facebook's servers, and only incentivize attacks against them. However, there
are many attackers that might feel uncomfortable attacking Facebook, but would
be willing to participate in attacks against other websites. In addition, having
only a single or small set of websites is a risk to DDoSCoin: if those websites
all go offline or successfully mitigate the attacks (such as by disabling TLS),
no future DDoSCoin blocks can be mined, and the currency will stall. At this
point, all DDoSCoins in circulation would become nearly worthless, as there
would be no way to safely transact them.

These issues lead to a few subtle requirements for choosing valid victims.
First, there must be \emph{limits} on who is allowed to be a victim, otherwise
miners can create local computational puzzles. At the same time, there must be
\emph{enough} targets in order to be robust against stalled blockchains.
Similarly, the list of victims must be \emph{flexible} in order to allow
removing targets as they become impractical to attack (either
through successful attack or mitigation), and adding new ones.

To address these issues, we propose two mechanisms the DDoSCoin protocol can
employ to allow victims to be selected by concensus.

@@

In order to allow victims to be (temporarily) selected for DoS, DDoSCoin
allows ``bounties'' for targetting specific servers. To accomplish this,
DDoSCoin introduces a new payment opcode, PAY\_TO\_DDOS, that can be used in
transactions subject to certain constraints. This opcode takes two arguments in
the output script: a
string representing a domain name that the payer wishes to have DDoSed, and a
target difficulty. Once this transaction is stored in a valid block, anyone can
collect its reward by creating a connection to the specified victim server, with
a response that meets the given target difficulty. These connections are made
similar to the way that miners connect to victim servers to create blocks, but
with a few important differences. First, the \texttt{client\_random} is
generated using the PAY\_TO\_DDOS transaction ID (txid), the SHA256 hash of the
output script the payee wants to collect the payment with, and a random nonce.
The client then makes connections to the specified victim domain until its
response meets the target difficulty
(SHA256(\texttt{server\_key\_exchange\_params} || \texttt{signature} ||
\texttt{nonce}) < target).

To collect the bounty reward, the client creates an input script that will
satisfy the PAY\_TO\_DDOS output. This includes the parameters of the
connection: the nonce, the \texttt{server\_random} value, the server's
certificate chain, the server key exchange parameters, and the server key
exchange signature. To validate the transaction, a miner must recompute the
\texttt{client\_random} using the transaction ID of the PAY\_TO\_DDOS
transaction, the hash of the output script in the claiming transaction, and the
nonce. Then, the miner must verify that the certificate is valid for the
provided domain (and rooted in a trusted CA), and that the certificate's
signature over the server key exchange message is valid. Finally, the server
must check that the server's response meets the target difficulty. If it does,
then the transaction is valid and can be included in a block.

There are a couple important features of this transaction. First, the reason the
transaction ID of the PAY\_TO\_DDOS transaction is included (committed to) in
the \texttt{client\_random} is to prevent a client from ``double-claiming''
multiple bounty rewards with the same proof-of-DoS. Similarly, the client
commits to the (hash of the) output script of the claiming transaction to
prevent others from being able to swap it for their own, therby ``stealing'' the
proof-of-DoS and collect the reward themselves. These combined allow two
mutaully-distrusting parties to directly and safely transact currency in
exchange for a DoS attack.

% client_random = H(txid || output_script || nonce)

%The transaction has no other parameters, but its value must be
%greater than the coinbase reward a miner would normally receive, and it must
%carry a non-negligble transaction fee. Once this transaction is stored in a
%valid block, the specified domain name is temporarily added to the list of
%allowed victims.  The first miner to mine a block with that domain as the victim
%must specify the PAY\_TO\_DDOS transaction as an input to its coinbase
%transaction (with any arbitrary output address), and have no other coinbase
%transactions. In other words, the miner collects the value in the PAY\_TO\_DDOS
%transaction in lieu of the normal block reward.
%
%The observant reader will notice that nothing stops the payer of the
%PAY\_TO\_DDOS transaction and the miner that it goes to from being the same
%entity. Indeed, a miner could create a PAY\_TO\_DDOS transaction with a victim
%domain that only it has access to, ensuring that it will be able to mine the
%block without competition, and collect its own payment. However, this will not
%net the miner new coins (\TK beyond any transaction fees collected? But we could
%make this block contain no transactions), as the coinbase transaction is
%replaced with its own PAY\_TO\_DDOS input.

While this new payment type allows a one-time payment for attacking a particular
target, it cannot be used to update the long-term victim list used by miners to
decide valid victims for blocks. Otherwise, miners could make a PAY\_TO\_DDOS
transaction specifying their own local domain in order to always have a
local-computation puzzle that allowed them to create new blocks in the future.
Instead, a second method for choosing victims must be employed.

%Instead, PAY\_TO\_DDOS must be a one-time only payment, allowing for the
%creation of a single block with a payment greater than the coinbase reward. This
%is similar to proof-of-burn, where new blocks can be created
%by miners proving that they have destroyed a certain amount of currency. The
%amount of currency in proof-of-burn cryptocurrencies is adjusted in the same way
%that difficulty is adjusted for proof-of-work to maintain a constant block rate.
%
%\paragraph{Concerns} Because it is possible for a miner to effectively pay a
%small fee to create a block that only they can solve quickly, PAY\_TO\_DDOS
%could irronically create a denial of service potential for DDoSCoin. To mitigate
%the risk of miners using PAY\_TO\_DDOS as a way to keep other miners from
%producing blocks, the amount above the coinbase reward a PAY\_TO\_DDOS
%transaction must pay is adjusted dynamically so that blocks that collect these
%transactions are not able to happen frequently. Additionally, these blocks do
%not contribute to the

@@

Proof-of-Stake to decide a delta on the victim-list.
